Turbulence in compact to giant HII regions

### 2022-06-16 strucfunc_paper.tex
Add sentence on M8 literature comparison

The structure function of the Lagoon Nebula was previously
studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
finding an approximate power law behavior (\(m = 0.46\))
on scales of \num{0.01} to \SI{0.2}{pc}.
No flattening of the structure function at the largest scales
was seen,
but that is to be expected due to the finite box effect
(see Appendix~\ref{sec:finite-box-effects})
given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
On the other hand, the magnitude of the velocity dispersion found by these authors much larger than we measure.
For instance, they find \(B(r) = \SI{278}{km^2.s^{-1}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-1}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
This may be due in part to the fact that \citet{Chakraborty:1999a}
observed a small and atypical part of the nebula known as the
Hourglass region, which includes a cluster of very young stars
\citep{Arias:2006e}.

>>>>

The structure function of the Lagoon Nebula was previously
studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
finding an approximate power law behavior (\(m = 0.46\))
on scales of \num{0.01} to \SI{0.2}{pc}.
No flattening of the structure function at the largest scales
was seen,
but that is to be expected due to the finite box effect
(see Appendix~\ref{sec:finite-box-effects})
given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
This may be due in part to the fact that \citet{Chakraborty:1999a}
observed a small and atypical part of the nebula known as the
Hourglass region, which includes a cluster of very young stars
\citep{Arias:2006e}. 
In the case of the Orion Nebula we found that the velocity dispersion
of the central region was larger than that of the extended nebula
and this could be an example of a similar phenomenon,
albeit to a more extreme degree.
